Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-26 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
without a clear definition. I tried to check its meaning from other
sources. In~\cite{Atmanspacher2014}, Atmanspacher defined `one
might paraphrase the deterministic yet non-determinable behavior of
such systems as ``cryptodeterminism,''' where ``deterministic''
and ``determinable'' is defined in the same section as `The recent
creation of the term ``deterministic chaos'' expresses the tension
between ontic (hidden) lawfulness and epistemic (apparent) irregularity
in chaotic system. Our description of the underlying laws of nature,
e.g. by differential equations governing the dynamics of such systems,
is no doubt deterministic, but their observable behavior is everything
but determinable (in the sense of measurable, computable, or predictable)
with arbitrary precision.' Is Atmanspacher's usage consistent with
Peres' and ours here?}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

@@

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
of the prefect prediction, a cryptodeterministic measure can model
the belief of events which has already happened. For example, if we
toss the coin in example~\ref{ex1}, and see $HH$, our belief of
which event has happened can be model by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
it was a famous question whether quantum mechanics have any change
to be improved and predict unambiguously, rather than probabilistic.
One way to formulate this question is to ask whether we can model
the whole quantum theory by quantum cryptodeterministic measures.

@@

The answer is ``no'' due to the Kochen-Specker theorem.

@@

Although sharing a lot of similarity, the Kochen-Specker theorem highlight
the difference between quantum and classical measures. When we think
a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
theorem also consistent with the usual interpretation of the quantum
theory: we should not ask whether an event happened or not if an event
is incompatible with the event really happened; events compatible
with the event really happened are the only events which are askable.

>>>>

\footnote{\yutsung{The word ''cryptodeterminism'' is used by Peres~\cite{peres1995quantum}
without a clear definition. I tried to check its meaning from other
sources. In~\cite{Atmanspacher2014}, Atmanspacher defined 
\begin{quote}
...one might paraphrase the deterministic yet non-determinable behavior
of such systems as ``cryptodeterminism''...
\end{quote}
where ``deterministic'' and ``determinable'' is defined in the
same section as 
\begin{quote}
The recent creation of the term ``deterministic chaos'' expresses
the tension between ontic (hidden) lawfulness and epistemic (apparent)
irregularity in chaotic system. Our description of the underlying
laws of nature, e.g. by differential equations governing the dynamics
of such systems, is no doubt deterministic, but their observable behavior
is everything but determinable (in the sense of measurable, computable,
or predictable) with arbitrary precision....
\end{quote}
Is Atmanspacher's usage consistent with Peres' and ours here?}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

@@

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
the prefect prediction, a cryptodeterministic measure can model the
belief of events which has already happened. For example, if we tossed
the coin in example~\ref{ex1}, and saw $HH$, our belief of which
event has happened can be model by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

\noindent The ability to predict classical events unambiguously rather
than probabilistic inspired Einstein, Podolsky, and Rosen to ask whether
quantum mechanics have any chance to be improved and predict in the
same way~\cite{EPR1935,peres1995quantum}. This question can be formulated
by whether the quantum mechanics could be modeled by quantum cryptodeterministic
measures.

@@

\noindent The answer is ``no'' due to the Kochen-Specker theorem.

@@

\noindent Although sharing a lot of similarity, the Kochen-Specker
theorem highlight the difference between quantum and classical measures.
When we think a cryptodeterministic measure as a model of pasted events,
the Kochen-Specker theorem also consistent with the usual interpretation
of the quantum theory: we should not ask whether an event happened
or not if an event is incompatible with the event really happened;
events compatible with the event really happened are the only askable
events.
